FoRTE baseline

### 2019-04-24 analysis/paper/paper.Rmd
Add draft of PEcAn-like parameter sensitivity analysis

Time series of aggregate variables (GPP, NPP, AGB, Total LAI), with error bars by structure

@@

Big facet plot (exploratory) of LAI by PFT for all model combinations

@@

@@

@@

## Parameter uncertainty

{TODO: PEcAn variance decomposition analysis, by configuration.}

Different parameter combinations produce qualitatively different successional outcomes.

>>>>

@@

Take-away: Parameter uncertainty is as large as, or even larger, than structural uncertainty.

@@

Take-away: Different parameter combinations produce not just quantitatively different bulk ecosystem properties (e.g. NPP, total LAI), but also qualitatively different successional/ecological outcomes.

@@

```{r uncertainty-analysis, fig.cap = uncertainty_analysis_cap, fig.dim = c(20, 15)}
uncertainty_analysis_cap <- paste(
  "PEcAn-liked parameter sensitivity and uncertainty analysis, by model type."
)
readd(sensitivity_plot)
```

`r mdcap(uncertainty_analysis_cap)`

@@
